{{< var titll >}}

### 2024-07-13 presentation.qmd
upd

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
modlat <- eqpar$meql
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))

round(polynom::integral(penf,c(0,1)),3)

per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
```

@@

Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
\begin{equation*}
g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
\end{equation*}

>>>>

```{r, echo=F, message=F, warning=F, results='hide'}
ManifoldDestiny::wasmconload()
modlat <- eqpar$meql
library(ManifoldDestiny)
laws_df1 <- ManifoldDestiny::eqdef$meql
laws_df2 <- ManifoldDestiny::eqdef$meqs
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/stylized.R'))
appnf <- seloutput(rppnf <- selreport(basc))
appr1 <- seloutput(rppr1 <- selreport(rigv[[1]]))
appr2 <- seloutput(rppr2 <- selreport(rigv[[2]]))
appr3 <- seloutput(rppr3 <- selreport(rigv[[3]]))
penf <- polynom::polynomial(unname(rppnf[[1]]$polyc[[1]][[1]],3))
per1 <- polynom::polynomial(unname(rppr1[[1]]$polyc[[1]][[1]],3))
per2 <- polynom::polynomial(unname(rppr2[[1]]$polyc[[1]][[1]],3))
per3 <- polynom::polynomial(unname(rppr3[[1]]$polyc[[1]][[1]],3))
#round(polynom::integral(penf,c(0,1)),3)
```

@@

Parameters: $g$, $h$, $\Gamma$, $\alpha$, $\Omega$
\begin{equation*}
g=`r modlat$g_h[1]` \text{, } h=`r modlat$h_h[1]` 
\end{equation*}
\begin{equation*}
\Gamma=`r modlat$Gamma_h[1]`
\end{equation*}
\begin{equation*}
\alpha=`r modlat$alpha_h[1]`=`r modlat$alpha_h[2]`
\end{equation*}
\begin{equation*}
\Omega=`r modlat$Omega_h[1] `=`r modlat$Omega_h[2]`
\end{equation*}
---
